---
title: "RNA-seq data preparation"
author: "Russ Poldrack"
date: "November 1, 2014"
output: html_document
---

This code loads the gene-level read count data and performs a variance-stabilizing transform using DESeq, and saves the resulting data for further analysis. First we must load the relevant libraries:

``` {r setup, message=FALSE}
library(DESeq)
library(vsn)
library("RColorBrewer")
library("gplots")

basedir='/Users/poldrack/data_unsynced/myconnectome/rna-seq'
```

####Load the data from the cloud and estimate size factors for correction
### use data that have been filtered for abundance (4>mean<10000) and removed snoRNAs
```{r loadData}
cdsFull=newCountDataSetFromHTSeqCount(read.table('http://s3.amazonaws.com/openfmri/ds031/RNA-seq/htcount_files.txt'),directory='http://s3.amazonaws.com/openfmri/ds031/RNA-seq/htcount_files_filtered')

cdsFull = estimateSizeFactors( cdsFull )
```

####Compute mean expression for each gene across sesssions
```{r computeMeans}
rs = rowMeans ( counts ( cdsFull ))
allgenes=rownames(counts(cdsFull))
```

####Remove genes with excessively high or low expression levels
```{r cleanGenes}
use = (rs>4 & rs<10000)
cds=cdsFull[use,]
usedgenes=rownames(counts(cds))
```

####Generate variance-stabilized count data and save to file
```{r varstab}
cdsBlind = estimateDispersions( cds, method="blind" ,fitType='local')
vsd = varianceStabilizingTransformation( cdsBlind )
vsdata=getVarianceStabilizedData(cdsBlind)
write.table(vsdata,sprintf('%s/varstab_data_prefiltered.txt',basedir))

```

####Plot dispersion estimates

```{r plotDispEsts}
plotDispEsts( cdsBlind )
```

####Plot SD vs. count before and after correction
```{r plotSD}
par(mfrow=c(1,2))
notAllZero = (rowSums(counts(cds))>0)
meanSdPlot(log2(counts(cds)[notAllZero, ] + 1), ylim = c(0,2.5))
meanSdPlot(vsd[notAllZero, ], ylim = c(0,2.5))
```


####Plot clusters of genes/sessions
```{r plotClustGenes}
select = order(rowMeans(counts(cdsBlind)), decreasing=TRUE)[1:30]
hmcol = colorRampPalette(brewer.pal(9, "GnBu"))(100)
heatmap.2(exprs(vsd)[select,], col = hmcol, trace="none", margin=c(10, 6))
```

#### Plot clusters of sessions - to look for outliers
```{r plotClustSessions}
dists = dist( t( exprs(vsd) ) )
mat = as.matrix( dists )
heatmap.2(mat, trace="none", col = rev(hmcol), margin=c(13, 13))

```




