---
title: "Run WGCNA"
author: "Russ Poldrack"
date: "November 1, 2014"
output: html_document
---

# Gene network analysis for MyConnectome data

This code loads the variance stabilized data (residualized against RIN and the first 3 PCs across subjects) and performs weighted gene coexpression network analysis (WGCNA).  See [the WGCNA page at UCLA](http://labs.genetics.ucla.edu/horvath/CoexpressionNetwork/) for more info on this technique.

```{r setup, echo=FALSE,message=FALSE,warning=FALSE,error=FALSE}
library(WGCNA)
allowWGCNAThreads(2)
options(stringsAsFactors = FALSE);
library(knitr)

basedir=Sys.getenv('MYCONNECTOME_DIR')
save_data=TRUE

outdir=sprintf("%s/rna-seq/WGCNA",basedir)

####Load the data
vsdata=read.table(sprintf('%s/rna-seq/varstab_data_prefiltered_rin_3PC_regressed.txt',basedir) )
datExpr=t(vsdata)
```


```{r pickThresh, echo=FALSE,message=FALSE}
#### Call the network topology analysis function

powers = c(c(1:10), seq(from = 12, to=20, by=2))
if (file.exists(sprintf('%s/sft.Rdata',outdir))) {
  load(sprintf('%s/sft.Rdata',outdir))
} else {
  sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5)
  if (save_data) {
    save(sft,file=sprintf('%s/sft.Rdata',outdir))
  }
}
```

#### Plot of network topology results to examine the scale-free topology metric:

```{r plotPickThresh, echo=FALSE,message=FALSE,warning=FALSE,error=FALSE}
par(mfrow = c(1,2));

cex1 = 0.9;

plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");

abline(h=0.90,col="red")

plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")


```

Based on these results, we choose power=8 to obtain fit of r^2~0.8


```{r runWGCNA, echo=FALSE,message=FALSE,warning=FALSE,error=FALSE}
##Run WGCNA estimation
if (!file.exists(sprintf('%s/net-thr8-prefilt-rinPCreg-48sess.Rdata',outdir))) {
  net = blockwiseModules(datExpr, power = 8,corType='bicor',
  TOMType = "unsigned", minModuleSize = 20,
  reassignThreshold = 1e-6, mergeCutHeight = 0.15,
  numericLabels = TRUE, pamRespectsDendro = FALSE,
  saveTOMs = FALSE,
  verbose = 3,maxBlockSize=4000)
  if (save_data) {
    save(net,file=sprintf('%s/net-thr8-prefilt-rinPCreg-48sess.Rdata',outdir))
    write.table(net$MEs, file=sprintf('%s/MEs-thr8-prefilt-rinPCreg-48sess.txt',outdir),row.names=FALSE,col.names=TRUE)
  }
} else {
  load(sprintf('%s/net-thr8-prefilt-rinPCreg-48sess.Rdata',outdir))
}


```

#### Plot WGCNA results

```{r plotResults, echo=FALSE,message=FALSE,warning=FALSE,error=FALSE}

mergedColors = labels2colors(net$colors)
plotDendroAndColors(net$dendrograms[[1]], mergedColors[net$blockGenes[[1]]],
"Module colors",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)

pdf(sprintf('%s/wgcna_tree.pdf',outdir))
mergedColors = labels2colors(net$colors)
plotDendroAndColors(net$dendrograms[[1]], mergedColors[net$blockGenes[[1]]],
"Module colors",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
dev.off()

```



```{r saveModAssn, echo=FALSE,message=FALSE,warning=FALSE,error=FALSE}
#### Save module assignments per gene
modules=as.data.frame(net$colors)
row.names(modules)=row.names(vsdata)
if (save_data) {
  write.table(modules,file=sprintf('%s/module_assignments_thr8_prefilt_rinPCreg.txt',outdir),col.names=FALSE,row.names=TRUE,quote=FALSE)
}
```

#### get hub genes using module membership (KME)

```{r saveHubGenes,results='asis', echo=FALSE,message=FALSE,warning=FALSE,error=FALSE}
skme=signedKME(datExpr,net$MEs)
hubgenes=c()
nhubs=5
for (i in 1:(ncol(skme)-1)) {
	kme=sprintf('kME%d',i)
	menum=which(names(skme)==kme)
	idx=order(skme[,menum],decreasing=TRUE)
	hubs=row.names(skme)[idx[1:nhubs]]
	hubgenes=rbind(hubgenes,c(names(skme)[menum],hubs))
	}
kable(as.data.frame(hubgenes))
if (save_data) {
  write.table(hubgenes,file=sprintf('%s/hubgenes_thr8_prefilt_rinPCreg.txt',outdir),col.names=FALSE,row.names=TRUE,quote=FALSE)
}


```

