---
title: "Metabolomics clustering"
author: "Russ Poldrack"
date: "November 1, 2014"
output: html_document
---

This is code for preprocessing of the metabolomics data for the MyConnectome study.

First, load the functions that will provide the data:

```{r setup}


basedir=Sys.getenv('MYCONNECTOME_DIR')

dataurl='http://web.stanford.edu/group/poldracklab/myconnectome-data/base/metabolomics'
save_data=TRUE
```

Load the data:

```{r loadData}
metab=load_metab_data(use_clustered_data=FALSE)
metab$date=NULL
metab=scale(metab)
```

The annotation tool that we will use requires PubChem IDs, so load those:

```{r loadCIDs}
cids=read.table(sprintf('%s/pubmed_cids.txt',dataurl))$V1
```


Set up the clustering tool:

```{r setupAP}
library(apcluster)
sim=corSimMat()
```

Run the clustering:

```{r runAP}
ap=apcluster(sim,t(metab))

ap
```

Save the clustering data and pubchem IDs for each cluster, for later use in annotation with Impala (set save_data=TRUE and change directory location to enable this)

```{r saveData}

if (save_data) {
  for (i in 1:length(ap@clusters)) {
    print(i)
  	for (member in 1:length(ap@clusters[[i]])) {
  		m=cids[ap@clusters[[i]]]
  		outfilename=sprintf('%s/metabolomics/apclust_scaled_mod%02d.txt',basedir,i)
  		write.table(m,file=outfilename,col.names=FALSE,row.names=FALSE,quote=FALSE)
    	outfilename=sprintf('%s/metabolomics/apclust_scaled_mod%02d_names.txt',basedir,i)
  		write.table(names(ap@clusters[[i]]),file=outfilename,col.names=FALSE,row.names=FALSE,quote=FALSE)

  		}
  	}
  save(ap,file=sprintf('%s/metabolomics/apclust.Rdata',basedir))
}
```

Compute eigenconcentrations for each cluster

```{r getEigenConc}

eigenconc=c()
meanconc=c()
for (c in 1:length(ap@clusters)) {
  print(c)
	cdata=metab[,ap@clusters[[c]]]
	pca=prcomp(cdata,retx=TRUE)
  pc=pca$x[,1]
  if (cor(pc,apply(cdata,1,mean)) < 0) {
    pc=pc*-1
  }
	eigenconc=cbind(eigenconc,pc)
  meanconc=cbind(meanconc,apply(cdata,1,mean))

	}
if (save_data) {
  write.table(eigenconc,sprintf('%s/metabolomics/apclust_eigenconcentrations.txt',basedir))
}
```
