---
title: "Metabolomics clustering"
author: "Russ Poldrack"
date: "November 1, 2014"
output: html_document
---

This is code for preprocessing of the metabolomics data for the MyConnectome study.

First, load the functions that will provide the data:

```{r}
source('http://s3.amazonaws.com/openfmri/ds031/timeseries_analyses/load_myconnectome_data.R')
```

Load and scale the data:

```{r}
metab=load_metab_data(use_clustered_data=FALSE)
metab$date=NULL
metab=scale(metab)
```

The annotation tool that we will use requires PubChem IDs, so load those:

```{r}
cids=read.table('http://s3.amazonaws.com/openfmri/ds031/metabolomics/pubmed_cids.txt')$V1
```


Set up the clustering tool:

```{r}
library(apcluster)
sim=negDistMat()
```

Run the clustering:

```{r}
ap=apcluster(sim,t(metab))

ap
```

Save the clustering data and pubchem IDs for each cluster, for later use in annotation with Impala (set save_data=TRUE and change directory location to enable this)

```{r}
save_data=FALSE
if (save_data) {
  for (i in 1:length(ap@clusters)) {
    print(i)
  	for (member in 1:length(ap@clusters[[i]])) {
  		m=cids[ap@clusters[[i]]]
  		outfilename=sprintf('/Users/poldrack/Dropbox/data/selftracking/proteomics/apclust_scaled_mod%02d.txt',i)
  		write.table(m,file=outfilename,col.names=FALSE,row.names=FALSE,quote=FALSE)
  		}
  	}
  save(ap,file='/Users/poldrack/Dropbox/data/selftracking/proteomics/apclust.Rdata')
}
```
