---
title: "Timeseries analyses for MyConnectome Project"
author: "Russ Poldrack"
date: "November 1, 2014"
output: html_document
---

# Timeseries analyses for MyConnectome dataset

Code available at: [https://github.com/poldrack/myconnectome/blob/master/myconnectome/timeseries/timeseries_analyses.Rmd](https://github.com/poldrack/myconnectome/blob/master/myconnectome/timeseries/timeseries_analyses.Rmd)

This notebook runs all of the timeseries analyses presented in the MyConnectome paper. The tables list all tests that survived at FDR-corrected p < 0.1, correcting within each set of tests.  

The variables listed in each table are:
- **xvar**:name of X variable
- **yvar**: name of Y variable
- **cor.val**: Pearson correlation between X and Y variables
- **t.arima**: *t* value from ARIMA model for X regressor
- **arima.p**: uncorrected *p* value from ARIMA model
- **t.drift**: *t* value from ARIMA model for drift parameter
- **drift.p**: *p* value from ARIMA model for drift parameter
- **AR**: autoregressive model order selected by automatic ARIMA model selection
- **MA**: moving average model order selected by automatic ARIMA model selection
- **nobs**: number of observations contributing to test (differs across tests due to missing data)
- **pval_bh**: p-value after Benajmini-Hochberg false discovery rate correction

```{r setup,message=FALSE,echo=FALSE, warning=FALSE}
library(forecast)
library(knitr)


basedir=Sys.getenv('MYCONNECTOME_DIR')

thresh=0.1  # FDR threshold
save_latex=TRUE
OUTPUT_DIR=sprintf('%s/timeseries',basedir)

```


```{r loadData, message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
behav=load_behav_data()
wincorr=load_fmri_data('wincorr')
bwcorr=load_fmri_data('bwcorr')
netdat=load_network_data()
fd=load_fd_data()
food=load_food_data()
rnaseq_wgcna=load_rnaseq_data(limit_ME_to_enriched=FALSE)
metab=load_metab_data()
pindex=load_participation_index()

data_names=c()
for (i in 1:(dim(metab)[2]-1)) {
    data_names=rbind(data_names,sprintf('C%d:%s',i,names(metab)[i]))
  	}
data_names=rbind(data_names,'date')
names(metab)=data_names


fullmetab=load_metab_data(use_clustered_data=FALSE)
data_names=c()
for (i in 1:(dim(fullmetab)[2]-1)) {
    n=gsub('_NIST','',names(fullmetab)[i])
    n=gsub('_',' ',n)

    data_names=rbind(data_names,n)
    }
data_names=rbind(data_names,'date')
names(fullmetab)=data_names


immport=load_ImmPort_data()

```


```{r behavSubset,echo=FALSE, warning=FALSE,message=FALSE}
# Create the subset of data that we are interested in for the behavioral analysis - generate a version without the tuesday/thursday variable for use with the blood data (which are only on tuesdays)

xvars=c('panas.positive','panas.negative','panas.fatigue','afterscan.Anxietyduringscan','afterscan.diastolic','afterscan.pulse','afterscan.systolic','morning.Sleepquality','morning.Soreness','prevevening.Alcohol','prevevening.Guthealth','prevevening.Psoriasisseverity','prevevening.Stress', 'prevevening.Timespentoutdoors','TuesThurs', 'temp.mean',"email.LIWCcdi","email.LIWCnegemo","email.LIWCposemo",'zeo.zq')

behav_keep=subset(behav,select=c(xvars,'date'))
behav_keep_no_tth=subset(behav_keep,select=-TuesThurs)
```


###  Behavioral variables vs. each other:

```{r BehavBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('behav','behav')
if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {
d=est_bivariate_arima_model(behav_keep, behav_keep,spacing='1 day',skip_ident=TRUE)
}
```

```{r  results="asis",echo=FALSE, warning=FALSE,message=FALSE}
kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  Within-module connectivity vs. behavior

```{r wincorrBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wincorr','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {
    d=est_bivariate_arima_model(wincorr,behav_keep)
    }
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### Between-module connectivity vs. behavior

```{r bwcorrBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('bwcorr','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(bwcorr,behav_keep)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### Network measures vs. behavior

```{r netdatBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('netdat','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(netdat,behav_keep)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### Participation index vs. behavior

```{r PIbehav,,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('pindex','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(pindex,behav_keep)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
print('skipping printout')

output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


### Behavior vs. RNA-seq:


```{r wgcnaBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wgcna','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna,behav_keep_no_tth,spacing='1 week')}
```


```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)


```

###  Within-module connectivity vs. RNA-seq
```{r wgcnaWincorr,,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wgcna','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna,wincorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  Between-module connectivity vs. RNA-seq
```{r wgcnaBwcorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wgcna','bwcorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna,bwcorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  Network measures vs. RNA-seq
```{r wgcnaNetdat,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wgcna','netdat')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna,netdat,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```



### ImmPort immune genes vs behavior

```{r immportBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('immport','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,behav_keep_no_tth,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  Test specific hypothesis regarding psoriasis
```{r psorImmport,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('psoriasis','immport')
psoriasis=subset(behav,select=c(date,prevevening.Psoriasisseverity))
if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,psoriasis,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  Test specific hypothesis regarding mood
```{r moodImmport,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('mood','immport')
mood=subset(behav,select=c(date,panas.positive,panas.negative))
if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,mood,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


### ImmPort immune genes vs within-module connectivity

```{r immportWincorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('immport','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,wincorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### ImmPort immune genes vs between-module connectivity

```{r immportBwcorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('immport','bwcorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,bwcorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### ImmPort immune genes vs network measures

```{r immportNetdat,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('immport','netdat')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,netdat,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### ImmPort immune genes vs food
```{r foodImmport,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('food','immport')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(food,immport,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### ImmPort immune genes vs metabolism
```{r immportMetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('immport','metab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,metab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### ImmPort immune genes vs metabolism (full set)
```{r immportFullmetab,,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('immport','fullmetab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(immport,fullmetab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```



###  food vs. metabolism
note: food needs to be X variable because auto.arima doesn't handle binary Y variable
```{r foodMetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('food','metab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(food,metab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  food vs. metabolism (individual metabolites)
note: food needs to be X variable because auto.arima doesn't handle binary Y variable
```{r foodFullmetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('food','fullmetab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(food,fullmetab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


###  behav vs. metabolsm
```{r behavMetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('behav','metab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(behav_keep_no_tth,metab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  behav vs. metabolsm (full set)
```{r behavFullmetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('behav','fullmetab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(behav_keep_no_tth,fullmetab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


### metabolism vs. within-network connectivity
```{r metabWincorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('metab','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(metab,wincorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### metabolism vs. within-network connectivity (full set of metabolites)
```{r fullmetabWincorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('fullmetab','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fullmetab,wincorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### metabolism vs. between-network connectivity
```{r metabBwcorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('metab','bwcorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(metab,bwcorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### metabolism vs. within-network connectivity (full set of metabolites)
```{r fullmetabBwcorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('fullmetab','bwcorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fullmetab,bwcorr,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

### metabolism vs. metabolism
```{r metabMetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('metab','metab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(metab,metab,skip_ident=TRUE,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


###  within-network connectivity 
```{r wincorrWincorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wincorr','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(wincorr,wincorr,skip_ident=TRUE)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  between-network connectivity 
```{r bwcorrBwcorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('bwcorr','bwcorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(bwcorr,bwcorr,skip_ident=TRUE)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
print('skipping printout')
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  within-network connectivity vs. network measures
```{r wincorrNetdat,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wincorr','netdat')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(wincorr,netdat)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  between-network connectivity vs. network measures
```{r bwcorrNetdat,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('bwcorr','netdat')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(bwcorr,netdat)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  network measures
```{r netdatNetdat,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('netdat','netdat')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(netdat,netdat,skip_ident=TRUE)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  food vs. within-network connectivity
```{r foodWincorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('food','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(food,wincorr)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  food vs. behavior
Remove food variables that have too many zeros or ones, otherwise will fail

```{r foodBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
food$apples=NULL  
food$blueberries=NULL
behav_keep_no_tth$zeo.zq=NULL

vnames=c('food','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(food,behav_keep_no_tth)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  compare head motion to other measures

###  FD vs. behavior
```{r fdBehav,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('fd','behav')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fd,behav_keep)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  FD vs. RNA-seq
```{r fdWgcna,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('fd','wgcna')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fd,rnaseq_wgcna,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  FD vs. metabolites

```{r fdMetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('fd','metab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fd,metab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  FD vs. wincorr
```{r fdWincorr,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('fd','wincorr')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fd,wincorr)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


###  FD vs. netdat
```{r fdNetdat,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('fd','netdat')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(fd,netdat)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  RNA-seq 


```{r wgcnaWgcna,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('wgcna','wgcna')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna, rnaseq_wgcna,spacing='1 week',skip_ident=TRUE)}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
# turning off output because there are too many significant results here - uncomment to turn it back on
#kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  RNA-seq vs. metabolism
```{r wgcnaMetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}
vnames=c('wgcna','metab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna,metab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

###  RNA-seq vs. metabolism (full set)
```{r wgcnaFullmetab,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('wgcna','fullmetab')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(rnaseq_wgcna,fullmetab,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```


###  RNA-seq vs. food


```{r foodWgcna,message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

vnames=c('food','wgcna')

if (file.exists(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))) {
  #print("loading existing file...")
  d=read.table(paste(OUTPUT_DIR,sprintf('out.dat.%s_%s.txt',vnames[1],vnames[2]),sep='/'))
  } else {d=est_bivariate_arima_model(food,rnaseq_wgcna,spacing='1 week')}
```

```{r  results="asis",message=FALSE,warning=FALSE,error=FALSE,echo=FALSE}

kable_wrap(d)
output_results(d,vnames,OUTPUT_DIR=OUTPUT_DIR)

```

